Demonstration of Effect of Indexing on\\ Cobb-Douglas and CES\\ Aggregate Production Functions

### 2017-01-19 Articles/Brockway_Landscape_2017/Indexing_Demo.Rnw
Using summary() now.

The coefficients for Cobb-Douglas models are shown below.
<<cd-coeffs>>=
cd_nonindexed
cd_indexed
@

@@

<<cd-logscale-to-theta>>=
exp(cd_nonindexed$coefficients[["logscale"]])
exp(cd_indexed$coefficients[["logscale"]])
@

@@

<<ces-coeffs>>=
ces_nonindexed
ces_indexed
@

>>>>

The coefficients for Cobb-Douglas models are shown below.
<<cd-coeffs>>=
summary(cd_nonindexed)
summary(cd_indexed)
@

@@

<<cd-logscale-to-theta>>=
exp(coef(cd_nonindexed)[["logscale"]])
exp(coef(cd_indexed)[["logscale"]])
@

@@

<<ces-coeffs>>=
summary(ces_nonindexed)
summary(ces_indexed)
@
